SatNOGS: Satellite~Networked~Open~Ground~Station

### 2015-08-27 paper.tex
tweaks

\documentclass[conference]{IEEEtran}

\usepackage{graphicx}
\usepackage[]{hyperref}
\hypersetup{
    letterpaper,
    colorlinks,
    urlcolor=blue,
    linkcolor=blue,
    citecolor=blue,
}

@@

@@

\author{
    \IEEEauthorblockN{Daniel J. White\IEEEauthorrefmark{1},
        SatNOGS Developers\IEEEauthorrefmark{2}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Valparaiso University, \href{mailto:dan.white@valpo.edu}{dan.white@valpo.edu}}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Libre Space Foundation,
    \href{mailto:info@satnogs.org}{info@satnogs.org}}

}

@@

\section{Introduction}
\IEEEPARstart{T}{he} SatNOGS\cite{SatNOGS} project seeks to build a full stack of open technologies for satellite ground stations.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\columnwidth]{fig/cubesat-launches}
\caption{CubeSat launches per year through 2015-07-17, from \cite{SwartwoutDatabase}.  The ``Commercial'' category includes non-profit and amateur satellites.}
\label{f:launches}
\end{figure}

@@

First proposed as a part of the 2014 International Space Apps Challenge's ``Virtual Ground Station App -- Global Crowdsourcing of CubeSats'' Challenge \cite{SpaceAppsChallenge2014-SatNOGS}, the SatNOGS project seeks to build such a network and community.
It was later submitted as an entry to the 2014 Hackaday Prize \cite{Hackaday-SatNOGS}, ultimately winning the grand prize of almost $\$200,000$.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\columnwidth]{fig/overall-system}
\caption{Overall view of the SatNOGS concept.}
\label{f:overall}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\columnwidth]{fig/four-components-titles-invert}
\includegraphics[width=\columnwidth]{fig/modular-options}
\caption{The four sub-projects are designed with a modular approach with well-defined interfaces, allowing the ability to relatively easily interface with existing ground stations.}
\label{f:modular}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\columnwidth]{fig/network-flow}
\caption{Diagram of a user scheduling an observation on the network.}
\label{f:network}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\columnwidth]{fig/client-flow}
\caption{Client software components and interactions.}
\label{f:client-flow}
\end{figure}

@@

\section{Ground Station}
The SatNOGS Ground Station sub-project encompasses the antennas, rotator, and RF path.
Ground station owners execute the Client software and build or configure the hardware.

>>>>

\documentclass[conference,12pt]{IEEEtran}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[]{hyperref}
\hypersetup{
    letterpaper,
    colorlinks,
    urlcolor=blue,
    linkcolor=blue,
    citecolor=blue,
}

@@

% consistent image widths
\newlength{\figwidth}
\setlength{\figwidth}{\columnwidth}
%\setlength{\figwidth}{4in}

\newcommand*{\pmzeroslash}{%
    \sbox0{0}%
    \sbox2{/}%
    \sbox4{%
      \raise\dimexpr((\ht0-\dp0)-(\ht2-\dp2))/2\relax\copy2 %
    }%
    \ooalign{%
      \hfill\copy4 \hfill\cr
      \hfill0\hfill\cr
    }%
    \vphantom{0\copy4 }% correct overall height and depth of the symbol
}

@@

% \IEEEauthorrefmark{1}
\author{
    \IEEEauthorblockN{Daniel J. White, Ph.D., AD\pmzeroslash CQ}
    %\IEEEauthorblockN{Daniel J. White, Ph.D., AD\O CQ}
    \IEEEauthorblockA{%
        Valparaiso University\\
        Valparaiso, Indiana\\
        \href{mailto:dan.white@valpo.edu}{dan.white@valpo.edu}}\\
    \and
    \IEEEauthorblockN{SatNOGS Developers}
    \IEEEauthorblockA{Libre Space Foundation\\
    \href{mailto:info@satnogs.org}{info@satnogs.org}}
}

@@

\section{Introduction}
\IEEEPARstart{T}{he} SatNOGS\cite{SatNOGS} project seeks to build a full stack of open technologies for satellite ground stations.
Blah foo bar asdfksadflsadfsad klsad flsadf sadfsadlkjfdsaf.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\figwidth]{fig/cubesat-launches}
\caption{CubeSat launches per year through 2015-07-17, from \cite{SwartwoutDatabase}.  The ``Commercial'' category includes non-profit and amateur satellites.}
\label{f:launches}
\end{figure}

@@

First proposed as a part of the 2014 International Space Apps Challenge's ``Virtual Ground Station App -- Global Crowdsourcing of CubeSats'' Challenge \cite{SpaceAppsChallenge2014-SatNOGS}, the SatNOGS project seeks to build such a network and community.
It was later submitted as an entry to the 2014 Hackaday Prize \cite{Hackaday-SatNOGS}, ultimately winning the grand prize of $\$196,418$.

% TODO:
\cite{Hackerspacegr}
\cite{Silver2015}
\cite{SatNOGS-Hamvention2015}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\figwidth]{fig/overall-system}
\caption{Overall view of the SatNOGS concept.}
\label{f:overall}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\figwidth]{fig/four-components-titles-invert}
\includegraphics[width=\figwidth]{fig/modular-options}
\caption{The four sub-projects are designed with a modular approach with well-defined interfaces, allowing the ability to relatively easily interface with existing ground stations.}
\label{f:modular}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\figwidth]{fig/network-flow}
\caption{Diagram of a user scheduling an observation on the network.}
\label{f:network}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\figwidth]{fig/client-flow}
\caption{Client software components and interactions.}
\label{f:client-flow}
\end{figure}

@@

\section{Ground Station}
The SatNOGS Ground Station sub-project encompasses the antennas, rotator, and RF path.
Ground station owners execute the Client software and build or configure the hardware.
Plans and instructions are available for the v2 ground station and are being finalized for the updated v3 version.
Gears and other parts are 3D printed and the rest of the hardware for the ground station is easily available.
Besides access to a 3D printer, only hand tools are required for building either version.
